Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-02 ms.tex
Sketching some in the discussion section.

% Figure~\ref{fig:vweff} shows an estimate of how the combined heating
% depends on the age of the stellar population $\tage$ and the SMB mass
% $\Mbh$.  For $M_{\bullet} \gtrsim 1.5\times 10^8 (\tau_{\star}/t_{\rm
%   h})^{0.5} \Msun$, SNe Ia occur sufficiently frequently within the
% stagnation radius (i.e., $r_{\rm Ia} > r_{\rm s}$; eq.~[\ref{eq:rIa}])
% to contribute their full heating rate.  $v_{w}^{\rm Ia} \sim
% 250$ km s$^{-1}$.  On the other hand, for lower mass BHs Ia SNe are
% infrequent, in which case main sequence stars ($v_{w}^{\star}
% \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of
% interest.\footnote{Although SN Ia will still occur surrounding low
%   mass SMBHs, if they are infrequent interior to the radius where the
%   accretion rate is being set, then they will not affect the flow near
%   the SMBH at most epochs.}  For very young stellar populations
% ($\tage \lsim 10^7$ years), $\vwO\simeq 1000$ km s$^{-1}$ due to
% contributions from line driven winds from high mass main sequence
% stars.
{\bf AG: We should mention that regime with stellar wind heating only
  is likely to be thermally unstable.}

@@

>>>>

% Figure~\ref{fig:vweff} shows an estimate of how the combined heating
% depends on the age of the stellar population $\tage$ and the SMB mass
% $\Mbh$.  For $M_{\bullet} \gtrsim 1.5\times 10^8 (\tau_{\star}/t_{\rm
%   h})^{0.5} \Msun$, SNe Ia occur sufficiently frequently within the
% stagnation radius (i.e., $r_{\rm Ia} > r_{\rm s}$; eq.~[\ref{eq:rIa}])
% to contribute their full heating rate.  $v_{w}^{\rm Ia} \sim
% 250$ km s$^{-1}$.  On the other hand, for lower mass BHs Ia SNe are
 infrequent, in which case main sequence stars ($v_{w}^{\star}
% \simeq 100-150$ km s$^{-1}$) dominate the heating at most times of
% interest.\footnote{Although SN Ia will still occur surrounding low
%   mass SMBHs, if they are infrequent interior to the radius where the
%   accretion rate is being set, then they will not affect the flow near
%   the SMBH at most epochs.}  For very young stellar populations
% ($\tage \lsim 10^7$ years), $\vwO\simeq 1000$ km s$^{-1}$ due to
% contributions from line driven winds from high mass main sequence
% stars.
{\bf AG: We should mention that regime with stellar wind heating only
  is likely to be thermally unstable.}

@@

\subsection{Nuclear Star Clusters}
Do nuclear star clusters in other galaxies look like scaled up/down
versions of the one in our own galaxy? If so this would imply a radial
gradient in the average of the stellar population which would imply a
heating which would be dependent on radius.

\subsection{SFR-AGN connection}
In fact it seems like the star formation rate may trace AGN
episodes. See e.g. http://arxiv.org/pdf/1501.07602.pdf.
